This is the Title

### 2017-03-08 trunk/abc/paper/paper.tex
Lovely and absurd trick for load16 tmp <- tmp
Implement 'Yet' CIL operator as improvement for dos2unix eqzero.c in translation of and/or boolean ops. Note a case where I'm generating non-printable bytes. Implement EqZero and NeZero throughout. Find that there's a bug somewhere, and made a good test case with eqzero.c
Fix a few bad bugs: Failure to clear knowledge of registers when they change leads to corrupt calculations, and cil initializing declaration would just initialize a different variable, ugh. Made tests one-liners so more fit on the screen.
Implement argc/argv, though they can't rea

>>>>

write about load16 tmp <- tmp; it's amazing now.
(benchmark history shows performance gains..)

words contained in this paper

``interrupt is a way of telling the operating system: Check this out!''

style points for:
- put relocations a little later after CS, so that we can mark
  with text the spot where they go.

opportunity for style points, like making your phone number into
a word:

 j ? X 4 ?   (4 can alternatively be $ or ,)

 NEED TO FIX:
  - some kind of output other than \_putc

 TOP PERFORMANCE IMPROVEMENTS:
  - don't jump at end of every block
  - don't assume a block needs to be split just because it's 0x7e-0x20.
    measure from the last jump!

dosbox patches, wing commander

ascii art in paper
